### 2014-07-29 paper/paper.tex
Wrote a bit for the baseline measure

A great deal of modern communications technologies allow people to discuss and
disseminate their opinions with a near negligible cost. Since the extremely low
cost allows everyone to share their opinions, the scale of textual data is
enormous. In order to gain insight into the `overall' opinion on particular
topics, the process of determining sentiment must be automated.

@@

Sentiment analysis is simply a classification task that attempts to label
fragments of text with a label that appropriately summarizes the attitude of
the text. Natural Language Processing (NLP) provides a number of method for
preforming sentiment analysis. Many of these methods take a probabilistic
approach to performing the task.

%TODO how could this be useful

@@

The classifier produced for this project is implemented in \textit{python} and make
extensive use of the \textit{nltk} (Natural Language Toolkit) library.

@@

After the SemEval-2013 workshop the organizers released a paper discussing the
proceedings and the results of the task.

%TODO

@@

@@

@@

>>>>

Social Media allows people to discuss topics and disseminate their opinions
with a near negligible cost. Since the cost of using social media is so low it
allows everyone to share their opinions as much as they please. Because of this
the scale of textual data is enormous. In order to gain insight into the
`overall' opinion on particular topics, the process of determining sentiment
must be automated.

@@

Sentiment analysis is simply a classification task that attempts to label
fragments of text with a label that appropriately summarizes the attitude of
the text. Natural Language Processing (NLP) provides a number of method for
preforming sentiment analysis. Many of these methods, such as Naive Bayes and
Maximum Entropy, take a probabilistic approach to performing the task. Another
commonly used method of performing sentiment analysis is the uses of a support
vector machine (SVM).

Performing sentimetn

@@

The classifier produced for this project is implemented in \textit{python} and
make extensive use of the \textit{nltk} (Natural Language Toolkit) library. As
well the implementation makes use of the \textit{flex} tool to create a lexer
for tokenization.

@@

@@

After the SemEval-2013 workshop the organizers released a paper discussing the
proceedings and the results of the task \cite{Nakov2013}. The paper establishes
baseline in terms of $F$. $F$ can be calculated $F = (F_{pos} + F_{neg}) / 2$
where $F_{pos} = 2 \frac{P_{pos}R_{pos}}{P_{pos} + R_{pos}}$ and $F_{neg}$ is
calculated in a similar fashion. The Precision measure for the positive label
is $P_{pos} = \frac{\mathrm{\# of\ true\ postive}}{\mathrm{\# of\ true\
postive} + \mathrm{\# of\ false\ postive} }$. The Recall measure for the
positive label is defined as $R_{pos} = \frac{\mathrm{\# of\ true\
postive}}{\mathrm{\# of\ true\ postive} + \mathrm{\# of\ false\ negative} }$

%TODO note that my solution is unconstrained

\subsection{Results}

\subsection{Comparison to Workshop Participants}

Table \ref{table:comparison} shows the performance of the classifier produced
for this project ranks compared to results of the workshop participants. The
full table (with out this project's results) can be found in table 9 of Nakov
et al. \cite{Nakov2013}.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Run & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of unconstrained classifiers by F-score}
    \label{table:comparison}
\end{table}

%TODO finsh table

@@

I am great and without reproach.

%TODO get a stronger conclusion

@@

As well Hashtags sometimes use CamelCase to create multi-word tags (e.g.
`\#SorryNotSorry'). It could prove worthwhile to attempt the decompose
CamelCase Hashtags into its component words during feature selection.
